SpARC: Sparse Redundant Calibration

### 2016-09-21 paper.tex
added novelty discussion to paper

\begin{enumerate}
 \item Present a general framework which unifies all the techniques developed so far showing they are all related (LINCAL, non-linear estimator, etc ...). They are all non-linear
 least-squares techniques, i.e. they either employ Gauss-Newton or the Levenberg-Marquardt algorithms. We have to start with LINCAL showing that it is GN, then we have to motivate 
 why we want to use Oleg's complex optimization framework.
 \item Use Oleg's complex optimization framework to re-derive the non-linear technique proposed by Marthi and Chengular. The novelty lies, in the fact that by using Oleg's
 framework we can find analytic expressions for the Jacobian, the Hessian and the Jacobian-residual product (which is not even the case for LINCAL). State that the algorithm is 
 effectively related to SteFCal and is eff an independent rediscovery of SteFCal and an extension of it into the redundant domain.
 \item Also we present the array geometry function to help us make the derivations from Marthi and Chengular easier to read and understand for a general layout.
 \item We also mention at this point that in Oleg's paper the question is raised is there a fast way of computing the exact inverse, we then present this new method, which is called
 conjugate gradient method. We discuss the algorithm and the two things which bound its execution time. Which is $kappa$ and $m$ (spectral condition number and its sparsity). Then
 we explore both of these parameters.
\end{enumerate}

>>>>

\begin{enumerate}
 \item Present a general framework which unifies all the techniques developed so far showing they are all related (LINCAL, non-linear estimator, etc ...). They are all non-linear
 least-squares techniques, i.e. they either employ Gauss-Newton or the Levenberg-Marquardt algorithms. We have to start with LINCAL showing that it is GN, then we have to motivate 
 why we want to use Oleg's complex optimization framework.
 \item Use Oleg's complex optimization framework to re-derive the non-linear technique proposed by Marthi and Chengular. The novelty lies, in the fact that by using Oleg's
 framework we can find analytic expressions for the Jacobian, the Hessian and the Jacobian-residual product (which is not even the case for LINCAL). State that the algorithm is 
 effectively related to SteFCal and is eff an independent rediscovery of SteFCal and an extension of it into the redundant domain.
 \item Also we present the array geometry function to help us make the derivations from Marthi and Chengular easier to read and understand for a general layout.
 \item We also mention at this point that in Oleg's paper the question is raised is there a fast way of computing the exact inverse, we then present this new method, which is called
 conjugate gradient method. We discuss the algorithm and the two things which bound its execution time. Which is $kappa$ and $m$ (spectral condition number and its sparsity). Then
 we explore both of these parameters.

 **************
 FLOW OF PAPER
 **************

 \begin{enumerate}
 \item We need the definition of visibilities as in Liu.
 \item Introduce the array geometery function.
 \item Write down logcal and lincal in matrix form... ?
 \item Short discussion of least squares and jacobian and hessian's. General GN and LM update rules.
 \item Introduce redundant calibration as a least squares problem.
 \item Propose a possible solution witch leads to lincal. Mention that this approach works as in this form the function is differentiable (a taylor expansion in the 
 parameters exists). Maybe mention that we can also divide the problem into real and imaginary etc...
 \item Show how this relates to lincal for example ---> show lincal is GN.
 \item Now introduce complex optimization ---> Main motivation for switching to the alternative framework is that the the differentials are very simplistic. We wish to show that
 we can derive the method of Chengular.
 \end{enumerate}

 We

 We neeed LOGCAL and LINCAL in matrix forms

\end{enumerate}
